Identifying covariate traits of trance and possession phenomena in the Ethnographic

### 2022-10-21 Readme.Rmd
working on paper in gdocs

```{r }
ld %>% 
  filter(var_title == 'Trance states', !is.na(code)) %>% 
  distinct(code, var_description) %>% 
  arrange(code) %>% 
  rename(coding = code, Description = var_description) %>% 
  kable('simple')
```

@@

Here is the distribution of the various descriptions for trance and possession in our training sample.

```{r }
trance = sccs %>% 
  filter(var_id == 'EA112') %>% 
  count(var_name,code,var_description) %>% 
  rename(name = var_name, description = var_description, count = n)

trance %>% 
  select(-code) %>% 
  add_row(name = 'Total', description = '', count = 151) %>% 
  kable('simple')
```

We see that only about 10% of societies have no trance or possession phenomena. From the rest, a majority have possession trance in some form. Following @bourguignon1968 we can reduce this to a binary: 81 societies have possession trance, 70 have other forms of trance and possessior or show neither.

```{r }
trance %>% 
  mutate(
    possession_trance = case_when(
      code %in% c(3,4,6,7) ~ 'possession trance',
      code %in% c(1,2,8,5) ~ 'other'
    ) %>% 
      fct_relevel('possession trance')
  ) %>% 
  group_by(possession_trance) %>% 
  summarise(count = sum(count)) %>% 
  kable('simple')
```

>>>>

```{r }
trance = sccs %>% 
  filter(var_id == 'EA112') %>% 
  count(var_name,code,var_description) %>% 
  rename(name = var_name, description = var_description, "n in SCCS" = n) %>% 
  mutate(
    possession_trance = case_when(
      code %in% c(3,4,6,7) ~ 'possession trance',
      code %in% c(1,2,8,5) ~ 'other'
    ) %>% 
      fct_relevel('possession trance')
  )

ld %>% 
  filter(var_title == 'Trance states', !is.na(code)) %>% 
  count(code, var_description, name = 'n in EA') %>% 
  left_join(trance) %>% 
  arrange(code) %>% 
  rename(Coding = code, Description = var_description) %>% 
  select(Coding,Description,possession_trance,`n in EA`,`n in SCCS`) %>% 
  kable('simple')
```

@@

Looking back at the table in the previous section, we see that only about 10% of societies have no trance or possession phenomena. From the rest, a majority have possession trance in some form. Following @bourguignon1968 we can reduce this to a binary: 81 societies have possession trance, 70 have other forms of trance and possessior or show neither.

```{r }
trance %>% 
  group_by(possession_trance) %>% 
  summarise(count = sum(`n in SCCS`)) %>% 
  kable('simple')
```
